Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-09-08 manuscript.Rmd
Amended information

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^2$, Joel T. Martin$^1$, Myat T. Aung$^1$, Alex R. Wade$^1$
 | & Daniel H. Baker$^1$
 | *eLife* (2023) https://doi.org/10.7554/eLife.87048
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
link-citations: true
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
- \usepackage{caption}
---

@@

# Author contributions

**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization. **Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition. **Joel Martin**: Software, resources, writing - review & editing. **Myat Aung**: Software, resources, writing - review & editing. **Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition. **Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.

>>>>

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^2$, Joel T. Martin$^1$, Myat T. Aung$^1$, Alex R. Wade$^1$
 | & Daniel H. Baker$^1$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
link-citations: true
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
- \usepackage{caption}
---

@@

### 2023-09-08 manuscript.tex
Amended information

\title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Joel T. Martin,\\
Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
Department of Psychology, University of York, UK\\
\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
\date{}

@@

\caption{Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
\end{figure}

@@

\caption{\label{tab:paramtable}Summary of median parameter values.}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
Data set & Z & k & w & Rmax\\
\hline
Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
\hline
EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
\hline
EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
\hline
Matching & 0.30 & 5.10 & 0.09 & -\\
\hline
\end{tabular}
\end{table}

@@

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization. \textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition. \textbf{Joel Martin}: Software, resources, writing - review \& editing. \textbf{Myat Aung}: Software, resources, writing - review \& editing. \textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition. \textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.

@@

\leavevmode\hypertarget{ref-Martin2023}{}%
Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M. 2023. PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and non-visual photoreception research. \emph{Journal of Vision} \textbf{In press}.

>>>>

\title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
\author{Federico G. Segala\(^1\), Aurelio Bruno\(^2\), Joel T. Martin\(^1\), Myat T. Aung\(^1\), Alex R. Wade\(^1\)\\
\& Daniel H. Baker\(^1\)}
\date{}

@@

\caption{Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 8). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
\end{figure}

@@

\caption{\label{tab:paramtable}Summary of median parameter values.}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
Data set & Z & n & w & Rmax\\
\hline
Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
\hline
EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
\hline
EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
\hline
Matching & 0.30 & 5.10 & 0.09 & -\\
\hline
\end{tabular}
\end{table}

@@

@@

\leavevmode\hypertarget{ref-Martin2023}{}%
Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M. 2023. PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research. \emph{Journal of Vision} \textbf{23}:10. doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
